Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-24 manuscript.Rmd
Updated abstract analysis figures. All functional.

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    mutate(N.prop = N/Overall.N) %>% group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N))

@@

journalOrder <- evidence.journalsOverall

ggplot(na.omit(evidence.journals), aes(N.prop, journal, group = journal, colour = studyType)) + geom_point(size = 3, alpha = .70) +
    theme_bw() +
    scale_colour_manual(values = cp) +
    facet_grid(.~studyType)

ggplot(na.omit(evidence.journals), aes(N, journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(alpha = .8, size = 3) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank())

>>>>

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    mutate(JN.prop = N/Overall.N) %>% group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N))

@@

df <-  select(evidence.journalsOverall, studyType, N, Overall.N.Strength) %>%
    rename(N.sort = Overall.N.Strength)

j.order <- unique(df$journal[order(df$N.sort, decreasing = FALSE)]) 
df$journal <- factor(df$journal, levels = j.order)

ggplot(na.omit(df), aes(x = N, y= journal, group = journal, colour = studyType)) + 
    geom_segment(aes(yend = journal), xend=0, colour="grey50") +
    geom_point(size = 2.5) + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    facet_grid(.~studyType) + 
    theme(panel.grid.major.y = element_blank())

evidence.journals <- full_join(evidence.summary3, evidence.summaryOverall, by = "journal") %>%
    group_by(journal) %>%
    mutate(Overall.N.Strength = sum(N)) %>%
    select(-studyType, N) %>%
    distinct(journal, Overall.N, Overall.N.Strength) %>%
    mutate(Prop = Overall.N.Strength / Overall.N)

df2 <- data.frame(evidence.journals)

j.order <- unique(df2$journal[order(df2$Prop, decreasing = FALSE)]) 
df2$journal <- factor(df2$journal, levels = j.order)

ggplot(na.omit(df2), aes(x = Prop, y= journal, group = journal)) + 
    geom_segment(aes(yend = journal), xend=0, colour="#b2abd2") +
    geom_point(aes(size = Overall.N.Strength), colour = "#5e3c99") + 
    scale_color_manual(values = cp) + 
    theme_bw() +
    theme(panel.grid.major.y = element_blank())
